### 2017-01-05 secorder-rdsa-ih.tex
experiments added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%% Quadratic case
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
\begin{enumerate}[label=(\textbf{C\arabic*}),resume]
\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and $\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
\end{enumerate}
\begin{theorem}(\textbf{Quadratic case - Convergence rate})
\label{thm:quad-bound}
Assume (C4), (C10), (C11) and (C12) and also that the setting is noise-free. 
Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
\begin{align}
\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
\label{eq:quad-bigo}
\end{align}
\end{theorem}
\begin{proof}
Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:hnhat} as follows:
\begin{align}
 \widehat H_n =    \Phi_n(\nabla^2 f(\theta_n)) &+\Psi_{n}(\nabla^2 f(\theta_n)),\label{eq:hnhat-ext}
\end{align}
where $\Psi_n(H)$ is defined in \eqref{eq:psi} and for any matrix $H$, 
$$\Phi_{n}(H) = [M_n]_{D}\left(d_{n}\tr \, [H]_{D} \, d_{n}\right) +  [M_n]_{N}\left(d_{n}\tr \, [H]_{N} \, d_{n}\right).$$
The proof involves the following steps:
\begin{description}
  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
  \item[Step 2:] We unroll the recursion \eqref{eq:2rdsa-H} and then derive convenient representation for $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
  \item[Step 3:] We derive the main result in \eqref{eq:quad-bigo} using a proof by contradiction. 
\end{description}
\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
\noindent\textbf{Step 2: Representation of $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$} \\
 From \eqref{eq:2rdsa-H} and \eqref{eq:hnhat-ext},  we have
 \begin{align}
 \Lambda_n &= \Lambda_{n-1} - b_n ( \overline H_{n-1} - \hat H_n + \hat \Psi_n) \nonumber\\
&= (1-b_n) \Lambda_{n-1} - b_n (H^* + \hat \Psi_n - \hat H_n ) \nonumber\\&= (1-b_n) \Lambda_{n-1} - b_n (H^*+\hat \Psi_n -\Phi_n(H^*) - \Psi_n(H^*)\nonumber\\&= (1-b_n) \Lambda_{n-1} - b_n \Psi_n(\Upsilon(\overline H_{n-1})) + b_n (\Phi_n(H^*) - H^*)\nonumber\\
&= (1-b_n) \Lambda_{n-1} - b_n\Psi_n(\Lambda_{n-1}')+ b_n (\Phi_n(H^*) - H^*),\label{eq:step1last}
 \end{align}
where $\Lambda_n' = \Upsilon(\overline H_n) - H^*$.
The equality in \eqref{eq:step1last} follows from \eqref{eq:psi}. 
Unrolling the recursion \eqref{eq:step1last}, we obtain 
 \begin{align}\label{lambda-exp}
  \Lambda_n  = \left[ \prod_{k=1}^n (1-b_k) \right]\Lambda_0 
&- \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right] b_k \Psi_k(\Lambda_{k-1}') \nonumber\\
&+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right] b_k (\Phi_k(H^*) - H^*) \hspace{0.2cm} a.s.
 \end{align}
 %%(note : $\prod_{j=n+1}^n (1-b_j) = 1$ for all n).
 %%Let us  characterise $trace[\E(\Lambda_n\tr \Lambda_n)]$ using \eqref{lambda-exp}. From independence of $d_k$ along k, \eqref{lambda-exp} represent martingale difference sequence, leading to 
Squaring on both sides and taking expectations, we obtain
 \begin{align}
  \E (\Lambda_n \tr \Lambda_n) =  &\left[ \prod_{k=1}^n (1-b_k) \right]^2 \E (\Lambda_0 \tr \Lambda_0) + \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \E (\Psi_k(\Lambda_{k-1}') \tr \Psi_k(\Lambda_{k-1}'))  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \times \E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*)) \nonumber\\
&-2 \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2 \E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right).\label{eq:exp-lambda2}
 \end{align}
The equality above uses the fact that $\E(\Psi_k(\Lambda_{k-1}'))=0$, $\E(\Phi_k(H^*) - H^*)=0$, which get rid of the corresponding cross terms with the first term on RHS of \eqref{lambda-exp}. Notice that there are only $n$ terms in the last term in the RHS of \eqref{eq:exp-lambda2} because $d_k$ are identically distributed for each $k$ and across $k$.  
% %
We now characterize $\text{trace}[\E(\Lambda_n\tr \Lambda_n)]$ using \eqref{eq:exp-lambda2} as follows:
%From the independence of $d_k$'s and $\Lambda_{k-1}'$ and using Cauchy-Schwartz inequality we get 
 \begin{align}\label{eq:trace}
 \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] = &\left[ \prod_{k=1}^n (1-b_k) \right]^2 \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  + \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]  \nonumber\\ &- 2 \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right].
 \end{align}

@@

% & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] \leq \left[ \prod_{k=1}^n (1-b_k) \right]^2 \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \nonumber\\&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] + \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2} \nonumber\\&  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.

@@

As in the proof of Theorem 3 of \cite{spall-jacobian}, observe that $1-b_k = e^{-b_k}(1-O(b_k^2))$ and since $0 < b_k <1$, we have that the $O(b_k^2)$ term is strictly positive. 
Letting $\Gamma_{ij} = \sum_{k=i}^j b_k$ with $\Gamma_{nn} = 1$ and $\beta_{kn} = \left[\prod_{i=k+1}^n (1- O(b_i^2))\right]^2$, we can simplify \eqref{eq:trace} as follows:
\begin{align}\label{eq:wij}
 \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] = &e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  + e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &- 2 e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2   \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right] .
 \end{align} 
% \begin{align}\label{eq:wij}
% & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] \leq e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \nonumber\\&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2} \nonumber\\&  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.

@@

Comparing the sum with integrals, we obtain
\begin{align*}
\Gamma_{ij} = \int_i^j \frac{b_0}{x^r} dx + O(1) &= \left(\frac{b_0}{1-r}\right)(j^{1-r}-i^{1-r}) +O(1),
\end{align*}
where we have used the facts that $0 < b_k < 1, \forall k \ge 2$ and 
$\sum_{k=i}^j b_k \to \infty$ as $j-i \to \infty$ since 
$b_k = b_0/k^r$ with $r > 0.5$.
Observing that $\beta_{kn}$ are uniformly upper-bounded, say by $\bar \beta_n$, we have
\begin{align}\label{eq:thmwts}
 & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] =  e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ 
&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}} \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &- 2 \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}   \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right].
\end{align} 
\begin{align}\label{eq:thmcomb}
& \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] =  e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ 
&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \text{trace}\left[\E [((\Phi_k(H^*) - H^*) - 2 \Psi_k(\Lambda_{k-1}))\tr  (\Phi_k(H^*) - H^*)]\right] .
\end{align} 

@@

%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}} \nonumber\\
%& \hspace{3.5cm} \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \nonumber\\
%&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \nonumber\\&\hspace{3.5cm}\times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2}\nonumber\\&\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.

@@

\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
In comparison to Eq. (7.6) in \cite{spall-jacobian} that corresponds to \eqref{eq:thmwts} for the N-SPSA-4 setting, there are two extra terms - the third and the fourth - in the RHS of \eqref{eq:thmwts}. 
Consider the third term on the RHS of \eqref{eq:thmwts}. As a consequence of (C9) and the construction of random perturbations $d_k$, it can be seen that $\text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]$ is uniformly bounded above, say by $\top$, independent of $k$. Thus, the third term is equivalent to the following:
\begin{align}
 \bar c_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \frac{b_0^2}{k^{2 r}} \top.
\label{eq:term3}
\end{align}
Now by moving out side exponential term to inside and changing the summation to integration, we can rewrite the above equation as follows
\begin{align}
  \overline{\overline{c_n}}  \int_1^n  \frac{1}{k^{2 r}} .
\label{eq:term3}
\end{align}
Where $\overline{\overline{c_n}}$ is a constant. By above equation we can conclude that the third term is of $O(\frac{1}{k^{2 r -1}})$
%Now, observe that $\lim_{n\rightarrow \infty} \sum_{k=1}^n \frac{1}{k^{2 r}} < \infty$ as $1/2 < r < 1$ and $e^{2 b_0 k^{1-r}/(1-r)}$ diverges as $n\rightarrow \infty$ and hence, by Kronecker's Lemma, the term in \eqref{eq:term3} vanishes asymptotically. 

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
%%%%%%%%%%%%%%%%%%%%%%%% Quadratic case
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%We next present a convergence rate result for the special case of a quadratic objective function under the following additional assumptions:
%\begin{enumerate}[label=(\textbf{C\arabic*}),resume]
%\item  $f$ is quadratic and $\nabla^2 f(x^*) > 0$. 
%\item The operator $\Upsilon$ is chosen such that $\E(\parallel \Upsilon(\overline H_n) - \overline H_n\parallel^2) = o(e^{-2wn^{1-r}/(1-r)})$ and $\parallel \Upsilon(H) - H \parallel^2 / (1+\parallel H \parallel^2)$ is uniformly bounded.
%\end{enumerate}
%\begin{theorem}(\textbf{Quadratic case - Convergence rate})
%\label{thm:quad-bound}
%Assume (C4), (C10), (C11) and (C12) and also that the setting is noise-free. 
%Let $b_n = b_0/n^r$, $n=1,2,\ldots,k$, where $1/2 < r < 1$ and $0 < b_0 \leq 1$. For notational simplicity, let $H^*=\nabla^2 f(x^*)$. Letting $\Lambda_k = \overline H_k - H^*$, we have 
%\begin{align}
%\text{trace}[\E (\Lambda_n \tr \Lambda_n)] = O(e^{-2b_0n^{1-r} / {1-r}}).
%\label{eq:quad-bigo}
%\end{theorem}
%\begin{proof}
%Since the setting is noise-free with a quadratic objective, we can rewrite \eqref{eq:hnhat} as follows:
%\begin{align}
% \widehat H_n =    \Phi_n(\nabla^2 f(\theta_n)) &+\Psi_{n}(\nabla^2 f(\theta_n)),\label{eq:hnhat-ext}
%where $\Psi_n(H)$ is defined in \eqref{eq:psi} and for any matrix $H$, 
%$$\Phi_{n}(H) = [M_n]_{D}\left(d_{n}\tr \, [H]_{D} \, d_{n}\right) +  [M_n]_{N}\left(d_{n}\tr \, [H]_{N} \, d_{n}\right).$$
%The proof involves the following steps:
%\begin{description}
%  \item[Step 1:] Here we prove the MSE convergence of $\overline H_k$, i.e., $\E [\Lambda_n\tr \Lambda_n] \rightarrow 0$ a.s. as $n\rightarrow \infty$.
%  \item[Step 2:] We unroll the recursion \eqref{eq:2rdsa-H} and then derive convenient representation for $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$.
%  \item[Step 3:] We derive the main result in \eqref{eq:quad-bigo} using a proof by contradiction. 
%\end{description}
%\noindent\textbf{Step 1: MSE convergence of $\overline H_n$} \\
%This part in exactly the same manner as part (i) in Theorem 3 of \cite{spall-jacobian}.\\
%\noindent\textbf{Step 2: Representation of $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$} \\
% From \eqref{eq:2rdsa-H} and \eqref{eq:hnhat-ext},  we have
% \begin{align}
% \Lambda_n &= \Lambda_{n-1} - b_n ( \overline H_{n-1} - \hat H_n + \hat \Psi_n) \nonumber\\
%&= (1-b_n) \Lambda_{n-1} - b_n (H^* + \hat \Psi_n - \hat H_n ) \nonumber\\&= (1-b_n) \Lambda_{n-1} - b_n (H^*+\hat \Psi_n -\Phi_n(H^*) - \Psi_n(H^*)\nonumber\\&= (1-b_n) \Lambda_{n-1} - b_n \Psi_n(\Upsilon(\overline H_{n-1})) + b_n (\Phi_n(H^*) - H^*)\nonumber\\
%&= (1-b_n) \Lambda_{n-1} - b_n\Psi_n(\Lambda_{n-1}')+ b_n (\Phi_n(H^*) - H^*),\label{eq:step1last}
%where $\Lambda_n' = \Upsilon(\overline H_n) - H^*$.
%The equality in \eqref{eq:step1last} follows from \eqref{eq:psi}. 
%Unrolling the recursion \eqref{eq:step1last}, we obtain 
% \begin{align}\label{lambda-exp}
%  \Lambda_n  = \left[ \prod_{k=1}^n (1-b_k) \right]\Lambda_0 
%&- \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right] b_k \Psi_k(\Lambda_{k-1}') \nonumber\\
%&+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right] b_k (\Phi_k(H^*) - H^*) \hspace{0.2cm} a.s.
% %%(note : $\prod_{j=n+1}^n (1-b_j) = 1$ for all n).
% %%Let us  characterise $trace[\E(\Lambda_n\tr \Lambda_n)]$ using \eqref{lambda-exp}. From independence of $d_k$ along k, \eqref{lambda-exp} represent martingale difference sequence, leading to 
%Squaring on both sides and taking expectations, we obtain
% \begin{align}
%  \E (\Lambda_n \tr \Lambda_n) =  &\left[ \prod_{k=1}^n (1-b_k) \right]^2 \E (\Lambda_0 \tr \Lambda_0) + \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \E (\Psi_k(\Lambda_{k-1}') \tr \Psi_k(\Lambda_{k-1}'))  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \times \E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*)) \nonumber\\
%&-2 \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2 \E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right).\label{eq:exp-lambda2}
%The equality above uses the fact that $\E(\Psi_k(\Lambda_{k-1}'))=0$, $\E(\Phi_k(H^*) - H^*)=0$, which get rid of the corresponding cross terms with the first term on RHS of \eqref{lambda-exp}. Notice that there are only $n$ terms in the last term in the RHS of \eqref{eq:exp-lambda2} because $d_k$ are identically distributed for each $k$ and across $k$.  
%% %
%We now characterize $\text{trace}[\E(\Lambda_n\tr \Lambda_n)]$ using \eqref{eq:exp-lambda2} as follows:
%%From the independence of $d_k$'s and $\Lambda_{k-1}'$ and using Cauchy-Schwartz inequality we get 

@@

% \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] = &\left[ \prod_{k=1}^n (1-b_k) \right]^2 \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  + \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]  \nonumber\\ &- 2 \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right].

@@

% % \begin{align}\label{eq:trace}
%% & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] \leq \left[ \prod_{k=1}^n (1-b_k) \right]^2 \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2  \nonumber\\&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] + \nonumber\\ &+ \sum_{k=1}^n \left[\prod_{j=k+1}^n (1-b_j)\right]^2 b_k^2   \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2} \nonumber\\&  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.
%% \end{align}
%As in the proof of Theorem 3 of \cite{spall-jacobian}, observe that $1-b_k = e^{-b_k}(1-O(b_k^2))$ and since $0 < b_k <1$, we have that the $O(b_k^2)$ term is strictly positive. 
%Letting $\Gamma_{ij} = \sum_{k=i}^j b_k$ with $\Gamma_{nn} = 1$ and $\beta_{kn} = \left[\prod_{i=k+1}^n (1- O(b_i^2))\right]^2$, we can simplify \eqref{eq:trace} as follows:
%\begin{align}\label{eq:wij}
% \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] = &e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  + e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &- 2 e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2   \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right] .

@@

%% \begin{align}\label{eq:wij}
%% & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] \leq e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \,\,\tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \nonumber\\&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &+ e^{-2 \Gamma_{1n}} \sum_{k=1}^n e^{2 \Gamma_{1k}} \beta_{kn} b_k^2  \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2} \nonumber\\&  \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.
%% \end{align} 
%Comparing the sum with integrals, we obtain
%\begin{align*}
%\Gamma_{ij} = \int_i^j \frac{b_0}{x^r} dx + O(1) &= \left(\frac{b_0}{1-r}\right)(j^{1-r}-i^{1-r}) +O(1),
%\end{align*}
%where we have used the facts that $0 < b_k < 1, \forall k \ge 2$ and 
%$\sum_{k=i}^j b_k \to \infty$ as $j-i \to \infty$ since 
%$b_k = b_0/k^r$ with $r > 0.5$.
%Observing that $\beta_{kn}$ are uniformly upper-bounded, say by $\bar \beta_n$, we have

@@

%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}} \times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &- 2 \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}   \times \text{trace} \left[\E\left(\Psi_k(\Lambda_{k-1}) \tr (\Phi_k(H^*) - H^*)\right)\right].

@@

%\begin{align}\label{eq:thmcomb}
%& \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] =  e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ 
%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \text{trace}\left[\E [((\Phi_k(H^*) - H^*) - 2 \Psi_k(\Lambda_{k-1}))\tr  (\Phi_k(H^*) - H^*)]\right] .
%%
%%\begin{align}\label{eq:thmwts}
%% & \text{trace} \left[\E (\Lambda_n \tr \Lambda_n)\right] =  e^{-2 \Gamma_{1n}} \beta_{0n} \text{trace} \left[\E (\Lambda_0 \tr \Lambda_0)\right]  \nonumber\\ 
%%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}} \nonumber\\
%%& \hspace{3.5cm} \times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)  \nonumber\\ 
%%&+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \nonumber\\
%%&  \hspace{0.5cm}\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right] \nonumber\\ &+ \bar \beta_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \times \frac{b_0^2}{k^{2 r}}  \nonumber\\&\hspace{3.5cm}\times \tau\left(\E (\Lambda_{k-1}' \otimes \Lambda_{k-1}')\right)^{1/2}\nonumber\\&\times \text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]^{1/2}.
%%\end{align}
%\noindent\textbf{Step 3: The big-O result on $\text{trace}[\E (\Lambda_n \tr \Lambda_n)]$ convergence} \\
%In comparison to Eq. (7.6) in \cite{spall-jacobian} that corresponds to \eqref{eq:thmwts} for the N-SPSA-4 setting, there are two extra terms - the third and the fourth - in the RHS of \eqref{eq:thmwts}. 
%Consider the third term on the RHS of \eqref{eq:thmwts}. As a consequence of (C9) and the construction of random perturbations $d_k$, it can be seen that $\text{trace}\left[\E ((\Phi_k(H^*) - H^*) \tr  (\Phi_k(H^*) - H^*))\right]$ is uniformly bounded above, say by $\top$, independent of $k$. Thus, the third term is equivalent to the following:
%\begin{align}
% \bar c_n e^{-2 b_0 n^{1-r}/(1-r)} \sum_{k=1}^n e^{2 b_0 k^{1-r}/(1-r)}  \frac{b_0^2}{k^{2 r}} \top.
%\label{eq:term3}
%Now by moving out side exponential term to inside and changing the summation to integration, we can rewrite the above equation as follows
